Cell Decompositions for Rank Two Quiver Grassmannians

### 2017-12-12 Grassmannian_cells.tex
Random edits

\documentclass{amsart}
\usepackage{amsmath,amssymb,latexsym,color}
\usepackage[bookmarks=true,colorlinks=true, linkcolor=blue, citecolor=cyan]{hyperref}
\usepackage{tikz}
\usepackage{pgflibraryarrows}
\usepackage{pgflibrarysnakes}
\usetikzlibrary{fit}
\usepackage[margin=1in]{geometry}
\usepackage{extarrows}
\usepackage{verbatim}
\input xy
\xyoption{all}

@@

\newcommand{\Ext}{\operatorname{Ext}}
\newcommand{\Hom}{\operatorname{Hom}}
\newcommand{\im}{\operatorname{im}}
\newcommand{\codim}{\operatorname{codim}}
\newcommand{\into}{\hookrightarrow}
\newcommand{\onto}{\to\!\!\!\!\!\to}
\newcommand{\ses}[3]{0\rightarrow #1\rightarrow #2\rightarrow#3\rightarrow 0}
\newcommand{\sesm}[4]{0\rightarrow #1\rightarrow #2\xrightarrow{#4}#3\rightarrow 0}
\newcommand{\Sc}[2]{\langle #1,#2\rangle}
\newcommand{\spn}{\operatorname{span}}
\setcounter{MaxMatrixCols}{20}
\newcommand{\vs}{\vspace{0.2cm}}
\hyphenation{endo-functors}

@@

-something about compatible pairs and combinatorial construction of cluster variables
-statement of our results
-something about torus actions and the universal cover
-something about cell decompositions of quiver Grassmannians
-acknowledgements?

@@

\begin{lemma}
  Every preprojective (resp. preinjective) representation of $Q$ can be lifted to  $\hat Q$ and $\tilde Q$.
\end{lemma}
\begin{proof}This statement is clear for the simple representations $S_q$, $q\in Q_0$. Now every preprojective representation $X$ can be obtained when applying a sequence of BGP-reflections \cite{bgp} to a simple representation $S_{q'}$ of a quiver $Q'$ whose underlying graph is the same as the one of $Q$. Applying BGP-reflections to a source $q$ of $Q$ corresponds to applying BGP-reflections to all vertices $(q,\chi)$ of $\hat Q$ (resp. $(q,w)$ of $\tilde Q$). This leads the claim. The statement for preinjective representations follows in the same way.
\end{proof}
As $F_Q$ and $G_Q$ are covering functors when restricting to one connected component, we obtain
\begin{theorem}\label{covering}
The functors $F_Q$ and $G_Q$ preserve indecomposability. Moreover, for all representations $\hat X,\hat Y \in\Rep(\hat Q)$, we have 
\[\Hom_Q(F_Q\hat X, F_Q\hat Y)\cong \bigoplus_{\chi\in A_Q}\Hom_{\tilde Q}(\hat X_\chi,\hat Y)\cong\bigoplus_{\chi\in A_Q}\Hom_{\tilde Q}(\hat X,\hat Y_\chi).\]
The analogous statement is true when replacing $\Hom$ by $\Ext$ and $\Rep(\hat Q)$ by $\Rep(\tilde Q)$ respectively.
\end{theorem}

Recall that every tuple of linear maps $(f_v:X_{s(v)}\to Y_{t(v)})_{v\in Q_1}$ defines a short exact sequence $\ses{Y}{Z}{X}$ with middle term defined by the vector spaces $Z_q=X_q\oplus Y_q$ for all $q\in Q_0$ and linear maps $Z_v=\begin{pmatrix}Y_v &f_v\\0&X_v\end{pmatrix}$ for all $v\in Q_1$. 
In general, considering the linear map  
\[d_{X,Y}:\bigoplus_{q\in Q_0}\Hom_k(X_q,Y_q)\to\bigoplus_{v\in Q_1}\Hom_k(X_{s(v)},Y_{t(v)}), (f_q)_{q\in Q_0}\mapsto(f_{t(v)}\circ X_{v}-Y_{s(v)}\circ f_{s(v)})_{v\in Q_1} \]
we have $\mathrm{ker}(d_{X,Y})=\Hom_Q(X,Y)$ and $\mathrm{coker}(d_{X,Y})=\Ext_Q(X,Y)$.

@@

The following is proved in \cite[Section 3]{cefr}.
\begin{theorem}\label{vb}
If the fibre dimension of $\Psi_\tbfe^{\tbff,\tbfg}$ is constant over $\mathrm{Im}(\Psi_\tbfe^{\tbff,\tbfg})$, then it an affine bundle over the image. In particular, the existence of a cell decomposition of $\mathrm{Im}(\Psi_\tbfe^{\tbff,\tbfg})$ implies a cell decomposition of $\cG_{\tbff,\tbfg}$ in this case.
\end{theorem}
%\begin{proof}\footnote{sketch, double-check}

%As $X$ and $Y$ are projective, they are compact. As the fibres are affine spaces of constant dimension and as $X$ and $Y$ are smooth, the induced morphism on the tangent spaces is surjective for all points $x\in X$. This shows that $f$ is smooth of relative dimension $n$, see Hartshorne and thus a submersion?!

%\end{proof}

@@

Define Chebyshev polynomials $u_k$ for $k\in\ZZ$ by the recursion $u_0=0$, $u_1=1$, $u_{k+1}=nu_k-u_{k-1}$.
The following is well-known.
\begin{theorem}
  \label{th:rigids}
  For each $m\ge1$, there exist unique (up to isomorphism) indecomposable rigid representations $P_m$ and $I_m$ of $K(n)$ with dimension vectors $(u_m,u_{m-1})$ and $(u_{m-1},u_m)$ respectively. 
  Moreover, any rigid representation of $K(n)$ is isomorphic to one of the form $P_m^{a_1}\oplus P_{m+1}^{a_2}$ or $I_m^{a_1}\oplus I_{m+1}^{a_2}$ for some $m\ge1$ and some $a_1,a_2\ge0$.
\end{theorem}
The representations $P_m$ are called the \emph{preprojective} representations of $K(n)$ and the representations $I_m$ are called \emph{preinjective}.
\begin{remark}\footnote{we should have $P_m=(\Sigma_iP_{m-1})^T$}
  \label{rem:reflection recursion}
  These representations satisfy the following recursions using the reflection functors:
  \[P_1=S_1,\quad P_m=\Sigma_2 P_{m-1},\quad I_1=S_2,\quad I_m=\Sigma_1 I_{m-1}\]
  for $m\ge2$.
  In particular, we have $P_{m-1}=\tau P_{m+1}$ and $I_{m+1}=\tau I_{m-1}$ for $m\ge2$. 
\end{remark}
%\begin{corollary}
%  \label{cor:preprojective stability}
%  For $m\ge1$ and $g\in G$, the representations $P_m$ and $g.P_m$ are isomorphic.
%\end{corollary}
%\begin{proof}
%  By construction, the representation $g.P_m$ also has dimension vector $(u_m,u_{m-1})$ and is indecomposable by Corollary~\ref{cor:indecomposability}.
%  Thus by Theorem~\ref{th:rigids}, $P_m$ and $g.P_m$ are isomorphic.
%\end{proof}
%For $g\in GL_n(\CC)$, write $\phi_{m,g}:P_m\to g.P_m$ for the (unique up to scalars) isomorphism from Corollary~\ref{cor:preprojective stability}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Quiver Grassmannians of $\widetilde{K(n)}$}\label{QG}
\noindent 
We fix a natural number $n\geq 3$. We fix the following lifts $\tilde P_m$  of $P_m$ to the universal cover $\widetilde{K(n)}$. For $m=1$ we assume that $\dim (\tilde P_1)_{1,1}=1$ and $\dim (\tilde P_m)_{i,w}=0$ if $(i,w)\neq (1,1)$. Moreover, we assume that $\dim (\tilde P_2)_{2,1}=\dim (\tilde P_2)_{1,w}=1$ for $w=a_1,\ldots,a_n$ and $\dim (\tilde P_2)_{i,w}=0$ if $(i,w)\notin\{(2,1),(1,a_1),\ldots,(1,a_n)\}$. Recall that applying the reflection functor $\Sigma_i$ on $K(n)$ corresponds to applying $\tilde\Sigma_i:=\prod_{w\in W_Q}\Sigma_{(i,w)}$ on $\widetilde{K(n)}$.  For $m\geq 3$, we can build lifts $\tilde P_m$ recursively by applying reflection functors or as Auslander-Reiten translation, i.e. we have
\begin{align}\label{recursive}\tilde P_m=(\tilde\Sigma_1 \tilde P_{m-1})^T,\quad\tilde P_{m+1}=\tau^{-1} \tilde P_{m-1}\text{ for }m\geq 2.\footnote{odd and even live on different components}\end{align}
Recall that we obtain the Auslander-Reiten translate $\tau^{-1}\tilde P_m$ by applying the reflection functor to the sinks twice where the sinks become sources after each step. 
\begin{remark}\begin{enumerate}
\item Note that the group $W_Q$ acts naturally on $\widetilde{K(n)}_0$ via translation, i.e. $w.(q,w')=(q,ww')$ inducing an action on $\Rep(\widetilde{K(n)})$. Up to this action a lift $\tilde P_m$ of $P_m$ is unique (on isomorphism classes).
\item Note that, the lifts $\tilde P_m$ all have the same middle vertex $(i,0)$ where $i=1$ is $m$ is odd and $i=2$ if $m$ is even.
\end{enumerate}
\end{remark}
The next step is to construct filtrations of $\tilde P_m$ by smaller preprojective $w.\tilde P_{l}$ for $l<m$ and certain $w\in W_Q$. To do so, we fix $m$ and the following notation can be seen as relative to $m$\footnote{do we need this?}.

Every representation $\tilde P_m$ has $n$ subrepresentation $\tilde P_{m-1,1},\ldots,\tilde P_{m-1,n}$. Each of them corresponds to one of the $n$ different arrows of $K(n)$. More precisely, we have 
$$\tilde P_{2l-1,i}:=a_i.\tilde P_{2l+1},\quad \tilde P_{2l,i}:=a_i^{-1}.\tilde P_{2l}$$
for all $l\geq 1$ and for $i=1,\ldots,n$. This can be checked straightforwardly for $l=1$ and follows in general when applying the identities (\ref{recursive}). In the following, we sometimes identify the arrows with the numbers $1,\ldots,n$.

We need some more notation in order to locate truncated preprojectives as quotients of other truncated preprojectives in the universal covering.
With every sequence of natural numbers $\ui=(i_1,\ldots,i_k)$ with $i_j\leq n$ and $k\leq m-1$, we can associate a preprojective subrepresentation $\tilde P_{m-k,\uj}$ of dimension $(u_{m-k},u_{m-k-1})$. More detailed, we obtain a sequence of preprojective representations 
$$\tilde P_{m-k,\ui}\subset P_{m-k+1,(i_1,\ldots,i_{k-1})}\subset\ldots\subset P_{m-1,(i_1,i_2)}\subset P_{m-1,i_1}\subset P_{m}.$$

Let
$$I^n_l:=\{(i_1,\ldots,i_{l})\mid i_j\in\{1,\ldots,n\},\,i_j\neq i_k\text{ if }j\neq k\}.$$
As we fixed the number of arrows, we drop the $n$ in what follows. For $\ui=(i_1,\ldots,i_{n-1})\in I_{n-1}$, let $i^c\in \{1,\ldots,n\}$ and $\ui^c=(i^c)$ where $i^c\neq i_j$ for $j=1,\ldots,n-1$. Clearly, $\ui^c$ is uniquely determined by $\ui$.

Let $(\underline{i_1},\underline{i_2},\ldots,\underline{i_r})$ be a sequence with $\underline{i_1}\in I_{n-1}$, $\underline{i_2},\ldots,\underline{i_{r-1}}\in I_{n-2}$ and $\underline{i_r}\in I_s$ for $s\leq n-2$. Define $i_1^c$ as before and for $k\geq 2$ let $i_k^c\in\{1,\ldots,n\}$ be the unique number such that $i_k^c\neq i_{k,j}$ for $j=1,\ldots,n-2$ and $i_k^c\neq i_{k-1}^c$. We say that $(\underline{i_1},\underline{i_2},\ldots,\underline{i_r})$ is admissible if 
$$ i_{k,j}\neq i_{k-1}^{c}\text{ for all }k=2,\ldots, r-1,\,j=1,\ldots,n-2\text{ and for }j=1,\ldots,s\text{ if }k=r.$$

For $\ui\in I_{s}$ with $s\leq n-1$, there exist unique exact sequences of the form
\[\ses{\bigoplus_{j=1}^s\tilde P_{m-1,i_j}}{\tilde P_m}{\tilde P_{m}^{\ui}},\quad\quad\ses{\tilde P_{m-1,i_s}}{\tilde P_{m}^{(i_1,\ldots,i_{s-1})}}{\tilde P_{m}^{\ui}}\]
where the $\tilde P_m^{\ui}$ are truncated preprojectives (as defined in the last section). The next step is to define a unique truncated preprojective representation for each admissible sequence ${\bf i}=(\underline{i_1},\underline{i_2},\ldots,\underline{i_r})$. We define the admissible sequence $\delta {\bf i}$ (of length $r-1$) by
\[\delta {\bf i}:=((i_1^c,\underline{i_2}),\ldots,\underline{i_r}).\]
We recursively define $\delta^l{\bf i}$ for $l=1,\dots,r-1$.
%In the following, we assume without loss of generality that $i_1< i_2<\ldots< i_k$.
Note that we have $\delta\ui=(i^c)$ for $\ui\in I_{n-1}$.

\begin{lemma}The following holds:
  \label{le:preprojective lifts}
  \begin{enumerate}
    \item $\Hom_Q(P_{m-1},P_m)\cong\bigoplus_{j=1}^n \Hom_{\tilde Q}(\tilde P_{m-1,j},\tilde P_m)$, where each $\Hom_{\tilde Q}(\tilde P_{m-1,j},\tilde P_m)$ is one-dimensional;
   % \item For any proper subset $\{i_1,\ldots,i_k\}\subset\{1,\ldots,n\}$, there exists a short exact sequence
   %   \[0\longrightarrow \tilde P_{m-1,i_1}\oplus\cdots\oplus\tilde P_{m-1,i_k}\longrightarrow\tilde P_m\longrightarrow \tilde P_m^{i_1,\ldots,i_k}\longrightarrow 0;\]
    \item The representations $\tilde P_{m,j}$ are pairwise orthogonal, i.e. for $j\neq i$ we have $$\Hom(\tilde P_{m-1,i},\tilde P_{m-1,j})=\Ext(\tilde P_{m-1,i},\tilde P_{m-1,j})=0;$$
    \item If $\ui\in I_{n-1}$ and $m\geq 3$, we have $\tilde P_{m}^{\ui}\cong \tilde P_{m-1,i^c}^{\ui^c}= P_{m-1,i^c}/P_{m-2,(i^c,i^c)}$.
		\item Let $m\geq 3$ and $1\leq r\leq m-1$ and let $\mathbf i:=(\underline{i_1},\ldots,\underline{i_r})$ be an admissible sequence. Let ${\bf i}(l):=(\underline{i_1},\ldots,\underline{i_l})$ for $l=2,\ldots,r-1$. Then we recursively have
		\[\tilde P_{m-l,(i_1^c,\ldots,i_l^c)}^{\delta^l{\bf i(l)}}=\tilde P_{m-l+1,(i_1^c,\ldots,i_{l-1}^c)}^{\delta^{l-1}\bf i(l)}\]
		for $l=1,\ldots,r$. Thus we can associate a unique truncated preprojective representation $$\tilde P^{\mathbf i}_{m-r+1}:=\tilde P_{m-r+1,(i_1^c,\ldots,i_{r-1}^c)}/\tilde P_{m-r+1,(i_1^c,\ldots,i_{r-1}^c)}^{(i_{r-1}^c,i_{r,1},\ldots,i_{r,s})}$$ with each admissible sequence ${\bf i}$.
  \end{enumerate}
\end{lemma}
\begin{proof}
The first statement follows from Theorem \ref{covering}. For $m=2$, the second part is obvious. For $m\geq 3$, it then follows by applying the identities (\ref{recursive}).

To prove the third part, we consider the following commutative diagram where the square on the left hand side is the corresponding Auslander-Reiten sequence:
\[\xymatrix{0\ar[r] &\bigoplus_{j=1}^{n-1}\tilde P_{m-1,i_j}\ar[r] &  \tilde P_{m}\ar[r] & \tilde P_{m}^{\ui}\ar[r] & 0 \\
  0\ar[r]&\tau\tilde P_m=\tilde P_{m-2} \ar[r]\ar[u] & \tilde P_{m-1,i^c}\ar[u]\ar[r]& \tilde P_{m}^{\ui}\ar[r]\ar@{=}[u]& 0}\]

%Thus we see that $\tilde P_{m}^{\ui}\cong \tilde P_{m-1}^{(l)}$ for some $l\in\{1,\ldots,n\}$. But now it is straightforward to check that $l=n$. \footnote{more precise?} 
For $m=3$, is straightforward that the injection of the lower row factors over $\tilde P_{1,i^c}$ which means that we get the same commutative diagram when replacing $\tilde P_{1}$ by $\tilde P_{1,(i^c,i^c)}$. Thus we have $\tilde P_{3}^{\ui}\cong \tilde P_{2,i^c}^{\ui^c}$. Applying the identities (\ref{recursive}) the claim follows for $m\geq 3$.

The forth statement is now obtained recursively when initially considering the diagram from above replacing $\ui$ by $\underline{i_1}$.

We have $\delta^{l-1}{\bf i}(l)=(i_{l-1}^c,i_{l,1},\ldots,i_{l,n-1})$. We use the third statement in order to successively obtain commutative diagrams
\[\xymatrix{0\ar[r] &\bigoplus_{j=1}^{n-2}\tilde P_{m-l,(i_1^c,\ldots,i_{l-1}^c,i_{l,j})}\ar[r] &  \tilde P^{(i_{l-1}^c)}_{m-l+1,(i_1^c,\ldots,i_{l-1}^c)}\ar[r] & \tilde P_{m-l+1,(i_1^c,\ldots,i_{l-1}^c)}^{\delta^{l-1}{\bf i}(l)}\ar[r] & 0 \\
  0\ar[r]&\tilde P_{m-(l+1),(i_1^c,\ldots,i_{l}^c,i_l^c)} \ar[r]\ar[u] & \tilde P_{m-l,(i_1^c,\ldots,i_{l}^c)}\ar[u]\ar[r]& \tilde P_{m-l,(i_1^c,\ldots,i_{l}^c)}^{(\underline{i_{l}^c)}}\ar[r]\ar@{=}[u]& 0}\]
Now we have $\delta^l{\bf i}(l)=(i_l^c)$.	Finally, we consider the short exact sequence:

\[\xymatrix{0\ar[r] &\bigoplus_{j=1}^{s}\tilde P_{m-r,(i_1^c,\ldots,i_{r-1}^c,i_{r,j})}\ar[r] &  \tilde P^{(i_{r-1}^c)}_{m-r+1,(i_1^c,\ldots,i_{r-1}^c)}\ar[r] & \tilde P_{m-r+1,(i_1^c,\ldots,i_{r-1}^c)}^{{\bf i}}\ar[r] & 0 }.\]
As $\Hom(\tilde P_{m-l,(i_1^c,\ldots,i_{l-1}^c,i_{l,j})},\tilde P_{m-l+1,(i_1^c,\ldots,i_{l-1}^c)})=k$ for all $l=2,\ldots,r$ and $i=1,\ldots,n-1$, applying the second statement, we obtain that the quotient $\tilde P_{m-r+1}^{\bf i}$ is uniquely determined.
	\end{proof}
We denote the quotient morphism by $\pi_m^{\bf i}:\tilde P_m\to \tilde P_{m-r+1}^{\bf i}$. It is important for us that this morphism factors through all truncated preprojectives $\tilde P_m^{(1,\ldots,l)}$ where $l\leq n-1$ and $j_k\neq i_1^c$ for $k=1,\ldots, l$. We also denote the quotient morphism from $\tilde P_m^{(j_1,\ldots,j_l)}$ to $\tilde P_{m-r+1}^{\bf i}$ by $\pi_m^{\bf i}$.

For convenience, we choose $\{j_1,\ldots,j_l\}=\{1,\ldots,l\}$, denote $\tilde P_m^{(l)}:=\tilde P_m^{(1,\ldots,l)}$ and define $\tilde P_m^{(0)}=\tilde P_m$ respectively. But we point out that the next statements also hold for general sequences $(j_1,\ldots,j_l)$ with the same proof. We need the following lemma analyzing the possible subrepresentations of truncated preprojective representations.
\begin{lemma}\label{le:subrep}
   All nontrivial proper subrepresentations $U$ of $\tilde P_m^{(1,\ldots,l)}$ are preprojective.	\footnote{Does it follow that the representations $F_{K(m)}\tilde P_m^{(j_1,\ldots,j_l)}$ are quasi-simple?}

\end{lemma}
\begin{proof}

We proceed by induction. Clearly $\tilde P_m$ has only preprojective subrepresentations. We can assume without loss of generality that the subrepresentation $U$ is indecomposable. Assume that $U\subsetneq P_m^{(l)}$ is not preprojective. Then the embedding would not factor through $\tilde P_m^{(l-1)}$ by induction hypothesis.  Thus we get a commutative diagram

\[\xymatrix{0\ar[r] &\tilde P_{m-1,l}\ar[r] &  \tilde P_{m}^{(l-1)}\ar[r] & \tilde P_{m}^{(l)}\ar[r] & 0 \\
  0\ar[r]&\tilde P_{m-1,l} \ar[r]\ar[u] & U'\ar[u]\ar[r]& U\ar[r]\ar[u]& 0}\]
where the vertical maps are injective, the sequence on the bottom does not split and the representation $U'$ is preprojective by induction hypothesis. Then we have $U\in\tilde P_{m-1,l}^\perp$
because $$\Hom(\tilde P_{m-1,l},U)=\Hom(\tilde P_{m-1,l},\tilde P_{m}^{(l)})=0.$$ Moreover, $\Ext(\tilde P_{m-1,l},U)=0$ follows because the representation $\tilde P_{m-1,l}$ is preprojective and $U$ is not. We also have $\Hom(U,\tilde P_{m-1,l})=0$ for the same reason.

As the sequence does not split, this shows that $U'$ is an indecomposable  (reference) preprojective subrepresentation of $\tilde P_{m}^{(l-1)}$. Since the only exceptional representations of $K(n)$ are preprojective, we have $\Sc{\udim U}{\udim U}\leq 0$. Thus, using  $\Sc{\udim U}{\udim \tilde P_{m-1,l})}< 0$, we obtain
\[\Sc{\udim U'}{\udim U'}=\Sc{\udim U}{\udim U}+\Sc{\udim \tilde P_{m-1,l} }{\udim \tilde P_{m-1,l} }+\Sc{\udim U}{\tilde P_{m-1,l}}\leq 1+\Sc{\udim U}{\tilde P_{m-1,l}}\leq 0.\]
But this contradicts the induction hypothesis because preprojective representations do not have self-extensions.

@@

  \end{enumerate}
\end{proposition}
\begin{proof}By Lemma \ref{le:subrep}.3, any subrepresentation $V\subsetneq \tilde P_{m+1}^{(k)}$ is preprojective. But the representation $\tilde P_{m,k}/U$ is not as it is a proper quotient of a preprojective representation unless $U=0$. Thus we have $\Ext(V,\tilde P_{m,k}/U)=0$. If $U=0$, we have $\Ext(V,\tilde P_{m,k})=0$ because for dimension reasons every indecomposable direct summand of $V$ is isomorphic to some $\tilde P_l$ with $l\leq m$.

>>>>

\documentclass{amsart}
\usepackage{amsmath,amssymb,latexsym,color}
\usepackage[bookmarks=true,colorlinks=true, linkcolor=blue, citecolor=cyan]{hyperref}
\usepackage{tikz}
\usepackage{pgflibraryarrows}
\usepackage{pgflibrarysnakes}
\usetikzlibrary{fit}
\usepackage[margin=1in]{geometry}
\usepackage{extarrows}
\input xy
\xyoption{all}

@@

\newcommand{\Ext}{\operatorname{Ext}}
\newcommand{\Hom}{\operatorname{Hom}}
\newcommand{\im}{\operatorname{im}}
\newcommand{\codim}{\operatorname{codim}}
\newcommand{\into}{\hookrightarrow}
\newcommand{\onto}{\to\!\!\!\!\!\to}
\newcommand{\ses}[3]{0\rightarrow #1\rightarrow #2\rightarrow#3\rightarrow 0}
\newcommand{\Sc}[2]{\langle #1,#2\rangle}
\newcommand{\spn}{\operatorname{span}}
\setcounter{MaxMatrixCols}{20}

\hyphenation{endo-functors}

@@

-something about compatible pairs and combinatorial construction of cluster variables\\
-statement of our results\\
-something about torus actions and the universal cover\\
-something about cell decompositions of quiver Grassmannians\\
-acknowledgements?\\

@@

\begin{lemma}
  Every preprojective and preinjective representation of $Q$ can be lifted to $\hat Q$ and $\tilde Q$.
\end{lemma}
\begin{proof}
  This statement is clear for the simple representations $S_i$, $i\in Q_0$.
  Now every preprojective or preinjective representation of $Q$ can be obtained by applying a sequence of BGP-reflections \cite{bgp} to a simple representation $S'_j$ of a quiver $Q'$ whose underlying graph is the same as the one for $Q$.
  Applying a BGP-reflection to a vertex $i$ of $Q$ corresponds to applying BGP-reflections to all vertices $(i,\chi)$ of $\hat Q$ (resp. $(i,w)$ of $\tilde Q$).
  This gives the claim.
\end{proof}
As $F_Q$ and $G_Q$ are covering functors when restricting to one connected component, we obtain
\begin{theorem}
  \label{covering}
  The functors $F_Q$ and $G_Q$ preserve indecomposability.
  Moreover, for all representations $\hat X,\hat Y \in\Rep(\hat Q)$, we have 
  \[\Hom_Q(F_Q\hat X, F_Q\hat Y)\cong \bigoplus_{\chi\in A_Q}\Hom_{\tilde Q}(\hat X_\chi,\hat Y)\cong\bigoplus_{\chi\in A_Q}\Hom_{\tilde Q}(\hat X,\hat Y_\chi).\]
  The analogous statements are true when replacing $\Hom$ by $\Ext$ or $\Rep(\hat Q)$ by $\Rep(\tilde Q)$.
\end{theorem}

Recall that every tuple of linear maps $(g_\alpha:X_{s(\alpha)}\to Y_{t(\alpha)})_{\alpha\in Q_1}$ defines a short exact sequence $\ses{Y}{Z}{X}$ with middle term defined by the vector spaces $Z_i=X_i\oplus Y_i$ for all $i\in Q_0$ and linear maps $Z_\alpha=\begin{pmatrix}Y_\alpha &g_\alpha\\0&X_\alpha\end{pmatrix}$ for all $\alpha\in Q_1$. 
In general, considering the linear map  
\[d_{X,Y}:\bigoplus_{i\in Q_0}\Hom_k(X_i,Y_i)\to\bigoplus_{\alpha\in Q_1}\Hom_k(X_{s(\alpha)},Y_{t(\alpha)}), (f_i)_{i\in Q_0}\mapsto(f_{t(\alpha)}\circ X_\alpha-Y_\alpha\circ f_{s(\alpha)})_{\alpha\in Q_1} \]
we have $\mathrm{ker}(d_{X,Y})=\Hom_Q(X,Y)$ and $\mathrm{coker}(d_{X,Y})=\Ext_Q(X,Y)$.

@@

The following is proved in \cite[Section 3]{cefr}.
\begin{theorem}\label{vb}
If the fibre dimension of $\Psi_\tbfe^{\tbff,\tbfg}$ is constant over $\mathrm{Im}(\Psi_\tbfe^{\tbff,\tbfg})$, then it an affine bundle over the image. In particular, the existence of a cell decomposition of $\mathrm{Im}(\Psi_\tbfe^{\tbff,\tbfg})$ implies a cell decomposition of $\cG_{\tbff,\tbfg}$ in this case.
\end{theorem}
\begin{proof}\footnote{sketch, double-check}

As $X$ and $Y$ are projective, they are compact. As the fibres are affine spaces of constant dimension and as $X$ and $Y$ are smooth, the induced morphism on the tangent spaces is surjective for all points $x\in X$. This shows that $f$ is smooth of relative dimension $n$, see Hartshorne and thus a submersion?!

@@

Define Chebyshev polynomials $u_k$ for $k\in\ZZ$ by the recursion $u_0=0$, $u_1=1$, $u_{k+1}=nu_k-u_{k-1}$.
The following is well-known.
\begin{theorem}
  \label{th:rigids}
  For each $m\ge1$, there exist unique (up to isomorphism) indecomposable rigid representations $P_m$ and $I_m$ of $K(n)$ with dimension vectors $(u_m,u_{m-1})$ and $(u_{m-1},u_m)$ respectively. 
  Moreover, any rigid representation of $K(n)$ is isomorphic to one of the form $P_m^{a_1}\oplus P_{m+1}^{a_2}$ or $I_m^{a_1}\oplus I_{m+1}^{a_2}$ for some $m\ge1$ and some $a_1,a_2\ge0$.
\end{theorem}
The representations $P_m$ are called the \emph{preprojective} representations of $K(n)$ and the representations $I_m$ are called \emph{preinjective}.
\begin{remark}
  \label{rem:reflection recursion}
  These representations satisfy the following recursions using the reflection functors:
  \[P_1=S_1,\quad P_m=\Sigma_2 P_{m-1},\quad I_1=S_2,\quad I_m=\Sigma_1 I_{m-1}\]
  for $m\ge2$.
  In particular, we have $P_{m-1}=\tau P_{m+1}$ and $I_{m+1}=\tau I_{m-1}$ for $m\ge2$. 
\end{remark}
%\begin{corollary}
%  \label{cor:preprojective stability}
%  For $m\ge1$ and $g\in G$, the representations $P_m$ and $g.P_m$ are isomorphic.
%\end{corollary}
%\begin{proof}
%  By construction, the representation $g.P_m$ also has dimension vector $(u_m,u_{m-1})$ and is indecomposable by Corollary~\ref{cor:indecomposability}.
%  Thus by Theorem~\ref{th:rigids}, $P_m$ and $g.P_m$ are isomorphic.
%\end{proof}
%For $g\in GL_n(\CC)$, write $\phi_{m,g}:P_m\to g.P_m$ for the (unique up to scalars) isomorphism from Corollary~\ref{cor:preprojective stability}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Quiver Grassmannians of $\widetilde{K(n)}$}\label{QG}
\noindent 
Let $\tilde P_m$ be a fixed lift of $P_m$ to the universal cover $\widetilde{K(n)}$. Note that the group $W_Q$ acts naturally on $\widetilde{K(n)}_0$ via translation, i.e. $w.(q,w')=(q,ww')$. Up to this action a lift $\tilde P_m$ of $P_m$ is unique. On the universal covering, every preprojective representation $\tilde P_m$ has $n$ subrepresentation $\tilde P_{m-1,1},\ldots,\tilde P_{m-1,n}$. Each of them corresponds (inductively) to one of the $n$ different arrows of $K(n)$. In turn, with every sequence of natural numbers $\uj=(j_1,\ldots,j_l)$ with $j_i\leq n$ and $l\leq m-1$ we can associate a preprojective subrepresentation $\tilde P_{m-k,\uj}$ of dimension $(u_{m-k},u_{m-k-1})$. For $\{i_1,\ldots,i_k\}\subset \{1,\ldots,n\}$ and $1\leq k\leq n-1$, there exist exact sequences of the form
\[\ses{\bigoplus_{j=1}^k\tilde P_{m-1,i_j}}{\tilde P_m}{\tilde P_{m}^{(i_1,\ldots,i_k)}},\quad\quad\ses{\tilde P_{m-1,i_k}}{\tilde P_{m}^{(i_1,\ldots,i_{k-1})}}{\tilde P_{m}^{(i_1,\ldots,i_k)}}.\]

Using this notation, we obtain the following lemma:
\begin{lemma}
  \label{le:preprojective lifts}
  \begin{enumerate}
    \item $\Hom_Q(P_{m-1},P_m)\cong\bigoplus_{i=1}^n \Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$, where each $\Hom_{\tilde Q}(\tilde P_{m-1,i},\tilde P_m)$ is one-dimensional;
   % \item For any proper subset $\{i_1,\ldots,i_k\}\subset\{1,\ldots,n\}$, there exists a short exact sequence
   %   \[0\longrightarrow \tilde P_{m-1,i_1}\oplus\cdots\oplus\tilde P_{m-1,i_k}\longrightarrow\tilde P_m\longrightarrow \tilde P_m^{i_1,\ldots,i_k}\longrightarrow 0;\]
    \item The representations $\tilde P_{m-1,i}$ are pairwise orthogonal;
    \item All nontrivial proper subrepresentations $U$ of $\tilde P_m^{(i_1,\ldots,i_k)}$ are preprojective.

  \end{enumerate}
\end{lemma}
\begin{proof}
The first statement follows from Theorem \ref{covering}. The second part follows for instance recursively by applying BGP-reflections.

For the third part, we proceed by induction. Clearly $\tilde P_m$ has only preprojective subrepresentations. We can assume without loss of generality that the subrepresentation $U$ is indecomposable. If $U\subsetneq P_m^{(i_1,\ldots,i_k)}$ were not preprojective, the embedding would not factor through $P_m^{(i_1,\ldots,i_{k-1})}$ by induction hypothesis.  Thus we get a commutative diagram

\[\xymatrix{0\ar[r] &\tilde P_{m-1,i_k}\ar[r] &  \tilde P_{m}^{(i_1,\ldots,i_{k-1})}\ar[r] & \tilde P_{m}^{(i_1,\ldots,i_{k})}\ar[r] & 0 \\
  0\ar[r]&\tilde P_{m-1,i_k} \ar[r]\ar[u] & U'\ar[u]\ar[r]& U\ar[r]\ar[u]& 0}\]
where the vertical maps are injective, the sequence on the bottom does not split and the representation $U'$ is preprojective by induction hypothesis. Then we have $U\in\tilde P_{m-1,i_k}^\perp$
because $$\Hom(\tilde P_{m-1,i_k},U)=\Hom(\tilde P_{m-1,i_k},\tilde P_{m}^{(i_1,\ldots,i_{k})})=0$$ and $\tilde P_{m-1,i_k}$ is preprojective and $U$ is not. Moreover, we have $\Hom(U,\tilde P_{m-1,i_k})=0$ for the same reason. Thus $U'$ is an indecomposable subrepresentation of $\tilde P_{m}^{(i_1,\ldots,i_{k})}$ (reference) such that
\[\Sc{\udim U'}{\udim U'}=\Sc{\udim U}{\udim U}+\Sc{\udim \tilde P_{m-1,i_k} }{\udim \tilde P_{m-1,i_k} }+\Sc{\udim U}{\tilde P_{m-1,i_k}}=1+\Sc{\udim U}{\tilde P_{m-1,i_k}}\leq 0\]
because we have $\Ext(U,\tilde P_{m-1,i_k})\neq 0$ as the bottom sequence does not split.
But this contradicts the induction hypothesis because preprojective representations do not have self-extensions.

@@

  \end{enumerate}
\end{proposition}
\begin{proof}By Lemma \ref{le:preprojective lifts}.3, any subrepresentation $V\subsetneq \tilde P_{m+1}^{(k)}$ is preprojective. But the representation $\tilde P_{m,k}/U$ is not as it is a proper quotient of a preprojective representation unless $U=0$. Thus we have $\Ext(V,\tilde P_{m,k}/U)=0$. If $U=0$, we have $\Ext(V,\tilde P_{m,k})=0$ because for dimension reasons every indecomposable direct summand of $V$ is isomorphic to some $\tilde P_l$ with $l\leq m$.
